---
title: "Week3 Assignment"
author: "Coffy Andrews-Guo"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

## R Character Manipulation and Date Processing 

Question 1
The 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], was pulled from [https://github.com/fivethirtyeight/data/blob/master/college-majors/majors-list.csv]


```{r pull_csv_file, include=TRUE}
library(readr)

urlfile = "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv"

majors <- read_csv(url(urlfile))
spec(majors)
```

Code identification of majors that contain either "DATA" or "STATISTICS"

```{r majors-DATA-STATISTICS}
library(stringr)

majors1 <- majors %>% 
  filter(str_detect(majors$Major, "DATA") | str_detect(majors$Major, "STATISTICS"))
majors1
```


Question 2
Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r data-transformation}

x <- c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")
print(x)
```


# The two exercises below are taken from R for Data Science, 14.3.5.1

Question 3
Describe, in words, what these expressions will match:

(.)\1\1
Response: This expression will match the same character appearing three times in a row.

"(.)(.)\\2\\1"
Response: This expression will match a pair of characters with the same pair of characters in reversed order.

(..)\1
Response: This expression wil match any two characters that are repeated. 

"(.).\\1.\\1"
Response: This expression will match any character followed by any character, the original character, any character, then the original character.

"(.)(.)(.).*\\3\\2\\1"
Response: This expression will match any three characters, followed by zero, then followed by the same three characters in a reverse order.


Question 4

Construct regular expressions to match words that:

Start and end with the same character.

Response: "^(.)((.*\\1$)|\\1?$)"

```{r}
library(stringr)
str_subset(words, "^(.)((.*\\1$)|\\1?$)")
```

Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
Response: "([A-Za-z][A-Za-z]).*\\1"

```{r}
str_subset(words, "([A-Za-z][A-Za-z]).*\\1")
```

Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
Response: "([a-z]).*\\1.*\\1"

```{r}
str_subset(words, "([a-z]).*\\1.*\\1")
```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


[RPubs](https://rpubs.com/blesned/808108)

[GitHub](https://github.com/candrewxs/W3_DATA607.git)

